Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-11-26 awipev-CO2.Rmd
script update text

###**FerryBox**
- **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.

>>>>

[Missing data to add to the NRT database](https://docs.google.com/spreadsheets/d/1Cbc4hWyclnBsNsOH_3QDA3AGZfwF4I1HuadfBe1BVjI/edit?usp=sharing)

[Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736)

### **FerryBox**
- **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.
